---
title: "STAT 420-finalproject"
author: "Siyu Niu Han Jiang Xinyi Peng Xingzhi Liu"
date: "2020/5"
output: html_document
---



```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
options(scipen = 1, digits = 4, width = 80)
library(knitr)
opts_chunk$set(cache = TRUE, autodep = TRUE)
```




# Financial and risk management in applied statistics with R




# Introduction 
The introduction section should relay what you are attempting to accomplish. It would include a statement of the business, science, research, or personal interest you have that leads to analyzing the data you’ve chosen. It should provide enough background to your work such that a reader would not need to load your data to understand your report. Like the simulation project, you can assume the reader is familiar with the course concepts, but not your data. Some things to consider:

What is this data? Where did it come from? What are the variables? Why is it interesting to you?
Why are you creating a model for this data? What is the goal of this model?


# Methods 

The methods section should contain the bulk of your “work.” This section will contain the bulk of the R code that is used to generate the results. Your R code is not expected to be perfect idiomatic R, but it is expected to be understood by a reader without too much effort. Use RMarkdown and code comments to your advantage to explain your code if needed.

This section should contain any information about data preparation that is performed to the original data before modelling. Then you will apply methods seen in class, which may include some of the following but are not limited to:

Multiple linear regression
Dummy variables
Interaction
Residual diagnostics
Outlier diagnostics
Transformations
Polynomial regression
Model selection
Your task is not to use as many methods as possible. Your task is to use appropriate methods to find a good model that can correctly answer a question about the dataset, and then to communicate your result effectively. Some possible items to be discussed:

Description of the original data file including description of all relevant variables.
Description of additional data preparation that you performed.
Description of the process you chose to follow.
Narrative of your step-by-step decision making process throughout the analysis as you adjusted the model and attempted to validate model assumptions.
```{r}
# install necessary packages
# install.packages("readxl")
```

```{r}
library(readr)
library("readxl")
```

# data clean

```{r}
The_interest_rate_for_the_United_States<- read_csv("The interest rate for the United States, from 2008 - 2018.csv")
plot(Volume ~ Date, data=The_interest_rate_for_the_United_States)
```

This dataset we will use the Volume and Adj Close columns.


```{r}
Dow_Jones_Industrial_Average_from_April <- read_csv("Dow Jones Industrial Average from April 2008 to April 2018.csv")
```

This dataset we will use the INTDSRUSM193N columns.

```{r}
Apple_Inc_company_stock <- read_csv("Apple Inc. - company stock.csv")
plot(Volume ~ Date, data=Apple_Inc_company_stock)
```
This dataset we will use the Adj Close and volume columns.

```{r}
Crude_Oil_price <- read_excel("Crude Oil Prices Daily.xlsx")
Crude_Oil_price$Date = as.Date(Crude_Oil_price$Date, format="%m/%d/%y")
plot(Closing_Price ~ Date, data=Crude_Oil_price)

Brent_Oil_price <- read_csv("BrentOilPrices.csv")
Brent_Oil_price$Date = as.Date(Brent_Oil_price$Date, format="%d-%b-%y")
plot(Price ~ Date, data=Brent_Oil_price)
```

# Results 
The results section should contain numerical or graphical summaries of your results. You should report a final model you have chosen. There is not necessarily one, singular correct model, but certainly some methods and models are better than others in certain situations. You may use any methods we studied this semester to complete this task, and provide evidence that your final choice of model is a good one. Some possible items to be discussed:


# Discussion
The discussion section should contain discussion of your results and should frame your results in the context of the data. How is your final model useful?

# Appendix
The appendix section should contain code and analysis that is used, but that would have otherwise cluttered the report or is not directly related to the choice of model. Do not simply dump code in here. Only utilize the appendix to supplement the primary focus of the report. The appendix should also conclude with the names of the group members.

Write in complete sentences and pay attention to grammar, spelling, readability and presentation. If you include a table or chart, make sure you say something about it. If you’re not discussing a result, then it doesn’t belong in your report.

Submit the following three items in a .zip file just as you do in homework assignments.

your selected data,
a .Rmd program file,
and the project report (.html file)
# Reference



